Introduction to Moltres: an Application for Simulation of Molten Salt Reactors

### 2017-08-01 Moltres.tex
passive to active

The effect of the advecting fuel is seen in \Cref{fig:temp} where the temperature
rises along the reactor height. As is expected, the temperature
gradient is negative in the radial direction.

>>>>

In \Cref{fig:temp} the temperature rises along the reactor height because of 
fuel advection. The temperature gradient is negative in the 
radial direction, as expected.
